Decomposing labelled proof theory for intuitionistic modal logic

### 2019-08-29 caleidoscope/caleidoscope.tex
working on extensions and soundness

	\begin{center}
		$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
	\end{center}

@@

@@

\todo{soundness sketch: general lemma? explain one or two rules?}

@@

\sonia{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}

\sonia{Scott-Lemmon with the new rules (general rules for F2, F1, etc) for the system and the lemma that shows that each rule is admissible}

@@

Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
%
These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.

\marianela{add the next proofs as extensions with Scott-Lemmon?}

@@

>>>>

	\begin{center}
		$\vlinf{\sorig}{}{\B, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\B, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
	\end{center}

@@

\begin{proof} [Proof for soundness]
	We need to prove that each sequent rule of our system $\labIKp$ is sound. As the proof is similar for each of the rules, we prove the soundness of some particular rules:

	\begin{itemize}
		\item Rule $\sbl$:

		We want to prove that the rule for $\sbl$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:

		\begin{center}
			\emph{For all model $\M$, if $\M \Vdash \B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$, then $\M \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$.}
		\end{center}

		By way of contradiction we want to see that if $\exists$ $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$,then $\M_{0} \not \Vdash premise$. More precisely for the $\sbl$ rule we want to show that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$ then $\M_{0} \not \Vdash \B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$.

		Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash x\colon \square A$ and  $\M_{0} \not \Vdash \Right$. Therefore, in particular, from $\M_{0} \Vdash \square A$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0},z \Vdash A$. Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$.

		\item Rule
	\end{itemize}
\end{proof}

@@

@@

\todo{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}

\todo{Scott-Lemmon with the new rules (general rules for F2, F1, etc) for the system and the lemma that shows that each rule is admissible}

The main goal of this section is to generate stronger logics adding new axioms to our system. We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.

@@

Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
%
These systems enjoy cut-elimination via usual arguments. Proofs of the the axioms we mentioned are below:

@@

The generality of the result adds a new rule to the system $\labIKp$ in order to capture the \emph{Scott-Lemmon axiom} or \emph{$\agklmn$ axiom}: 
\begin{center}
	$\lozenge^{k} \square^{l} A \vljm \square^{m}\lozenge^{n} A$
\end{center}
Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:

$\star$ \emph{Classical case} \hspace{2.2mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$

$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \vljm \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\

See this axiom in the Figure~\ref{fig:gklmn} \todo{Wrong label}

\begin{figure}[h]
	\begin{center}
		$
		\xymatrix{
			& u' \ar@{.>}[ddr]^{R^l} \\
			& u \ar@{.>}[u]^{\le} \\
			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
			& v \ar@{.>}[ur]_{R^n}
		}
		$
	\end{center}
	\label{fig:gklmn}
	\caption{$\agklmn$ axiom for intuitionistic case}
\end{figure}
